---
title: "Shiny Application and Reproducible Pitch"
author: "Juan A. Reyes D."
date: "8/4/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This presentation contains documentation about the Shiny Application and Reproducible Pitch as part of a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization. This assignment has two parts:
 
Shiny application. You can the source code for ui.R and server.R files are available on the GitHub repo <https://github.com/juanreyesduran/DS-Data_Products_Assignment3>

Reproducible pitch presentation about Shiny application that you can see on <http://rpubs.com/juanreyesduran/378012>

## Web Application Funcionality

The sites is providing sidebar with controls to select the random distribution type 
- Normal 
- Uniform
- Log-Normal
- Exponential

and number of observations is required and then plotted as a histogram.


## Histogram

```{r}
data <- rnorm(1000,0,1)
hist(data, main="rnorm(1000)", cex.axis=.8, xlim=c(-4,4), col="green")
```
